---
title: "Quantitiative Growth Curve Evaluation with Package `QurvE`"
author: "Nicolas T. Wirth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quantitiative Growth Curve Evaluation with Package `QurvE`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/research-institute-for-nature-and-forest.csl
link-citations: true
lang: en-US
zotero: true
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<strong>Please note:</strong> This vignette will be updated from time to time when new features are implemented. Please find the most recent version at the [QurvE GitHub repository](https://github.com/NicWir/QurvE).

# Introduction

In virtually all disciplines of biology dealing with living organisms, from classical microbiology to applied biotechnology, it is routine to characterize the **growth** of the species under study. `QurvE` provides a suite of analysis tools to make such growth profiling quick, efficient, and reproducible. In addition, it allows the characterization of **fluorescence** data for, e.g., biosensor characterization in plate reader experiments (further discussed in the vignette *Quantitiative Fluorescence Curve Evaluation with Package `QurvE`)*. All computational steps to obtain an in-depth characterization are combined into user-friendly *workflow* functions and a range of plotting functions allow the visualization of fits and the comparison of organism performances.

Any physiological parameter calculated (e.g., growth rate µ, doubling time t~D~, lag time $\lambda$, density increase $\Delta$Y, or equivalent fluorescence parameters) can be used to perform a dose-response analysis to determine the *half-maximal effective concentration* (EC~50~).

The package is build on the foundation of the two R packages from @kahm2010 and @petzoldt2022. With consideration for `R` novices, it establishes a framework in which a complete, detailed growth curve analysis can be performed in two simple steps:

1.  *Read data* in custom format or parse data from a plate reader experiment.

2.  *Run workflow*, including fitting of growth curves, dose-response analysis, and rendering a report that summarizes the results.

All computational results of a workflow are stored in a data container (list) and can be visualized by passing them to the generic function `plot(list_object)`. `QurvE` further extends the user's control over the fits by defining thresholds and quality criteria, adds

# Growth profiling methods

Three methods are available to characterize growth curves:

1.  Determine maximum growth rates (µ~max~) from the log-linear part of a growth curve using a heuristic approach proposed as the "growth rates made easy"-method by @hall2014. Do do so, `QurvE` uses code from the package @petzoldt2022, but adds user-defined thresholds for (i) R^2^ values of linear fits, (ii) relative standard deviations (RSD) of estimates slopes, and (iii) the minimum fraction of total density increase ($\Delta$Y) a regression window should cover to be considered for the analysis. These thresholds ensure a more robust and reproducible identification of the linear range that best describes the growth curve. Additionally, parameters for a *secondary growth phase* can be extracted for bi-linear growth curves.[^1]
2.  Perform a smooth spline fit on (log-transformed) growth data and extract µ~max~ as the maximum value of the first derivative^1^.

[^1]: For linear and nonparametric (i.e, smooth spline) fits, the lag time is calculated as the intersect of the tangent at µ~max~ and a horizontal line at the first data point (y~0~). For the analysis of biphasic growth curves, the lag time is extracted as the lower of the two obtained values.

<!-- -->

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side.

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes[^2], and tables, e.g. using `knitr::kable()`.

[^2]: A footnote here.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither." ([via](https://twitter.com/hadleywickham/status/504368538874703872))
